The very dependent recursive structure of iterated parametricity in indexed form

### 2025-12-29 paper/paper.tex
paper: minor paragraph section

In \cite{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity. That is, instead of the following illustration of the semi-cubical case (upto faces identities),

>>>>

\paragraph*{Iterated parametricity in indexed form.}
In \cite{hr25}, this correspondence was exploited to construct at the same time augmented semi-simplicial and semi-cubical sets in \emph{indexed form} as a special case of iterated parametricity. That is, instead of the following illustration of the semi-cubical case (upto faces identities),
